Incorporating Weighted Clustering in 3D Gesture Recognition

### 2011-12-17 paper/paper.tex

\title{Incorporating Gyroscope Information in Gesture Recognition}
\author{
        John Hiesey \\
        jhiesey@cs.stanford.edu
        \and
        Clayton Mellina \\
        cmellina@cs.stanford.edu
        \and
        Zavain Dar \\
        zdar@cs.stanford.edu
}
\date{\today}

@@

\section{Conclusions}\label{conclusions}
We thus show non trivial gains in accuracy with resect to our baseline classifier KHMM.  These gains are accrued not only through the collection of a new set of features using gyroscope data, but also through our novel algorithms Cluster-Matching-HMM and Cluster-Matching.  Interestingly enough it appears that even though we are classifying sequential data, simply assigning cluster fitness scores to all the vectors in a gesture example, regardless of sequential order, returns the most accurate classifiers.  In fact, the only times when this is not the case is when we synthetically manipulate the data files to purposely break our Cluster-Matching classifier.  However, we could not mimic this ``break case" using actual gesture data.  We are thus confident in the ability of Cluster-Matching to accurately classify real human gestures.  Regardless, we hope to have pushed forward the study and field of gesture recognition; not only by presenting classifiers with high accuracy, but also through the presentation of a new cluster based paradigm of classifiers.

>>>>

\title{Incorporating Weighted Clustering in 3D Gesture Recognition}
\author{
        John Hiesey \\
        jhiesey@cs.stanford.edu
        \and
        Clayton Mellina \\
        cmellina@cs.stanford.edu
        \and
        Zavain Dar \\
        zdar@cs.stanford.edu
}
\date{\today}

@@

\section{Conclusions}\label{conclusions}
We thus show non trivial gains in accuracy with resect to our baseline classifier KHMM.  These gains are accrued not only through the collection of a new set of features using gyroscope data, but also through our novel algorithms Cluster-Matching-HMM and Cluster-Matching.  Interestingly enough it appears that erven though we are classifying sequential data, simply assigning cluster fitness scores to all the vectors in a gesture example, regardless of sequential order, returns the most accurate classifiers.  In fact, the only times when this is not the case is when we synthetically manipulate the data files to purposely break our Cluster-Matching classifier.  However, we could not mimic this ``break case" using actual gesture data.  We are thus confident in the ability of Cluster-Matching to accurately classify real human gestures.  Regardless, we hope to have pushed forward the study and field of gesture recognition; not only by presenting classifiers with high accuracy, but also through the presentation of a new cluster based paradigm of classifiers.
